---
title: "Pyraclostrobin_Amphibian"
author: "Alex Dhond"
date: "11/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script develops and plots amphibian SSDs for pyraclostrobin using both surrogate and prediction data. The data was provided by Annie and Tom. 

# Set working directory
```{r}
# Set working directory to file location
setwd('C:/Users/epauluko/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/GitHub/amphibian_effects_model')
```

# Clear existing workspace
```{r}
# Clear existing workspace
rm(list=ls())
```

# Load required packages
```{r}
library(dplyr) # Used for data manipulation
library(tidyr) # data manipulation
library(data.table) # Used for creating data tables
library(EnvStats) # Used for calculating geometric means
library(fitdistrplus) # for fitting various distributions to the data
library(flexsurv) # for fitting parametric distributions
library(ggplot2) # for plotting
library(readxl) # read in excel sheets
```

# Load in the source data
Load in amphibian data from the Excel sheet
```{r}
# Read in the amphibian data
data <- readxl::read_xlsx("data_in/AqICE_PredAmphib_PyraGlypho (003).xlsx")
```

# Clean up data and filter for SSD model
Extract relevant columns, rename them, remove NAs, and filter only Pyraclostrobin
```{r}
# Extract only relevant columns
data <- data[, c(1:4,7)]

# Rename columns
colnames(data) <- c("Chemical", "Surrogate", "Prediction", "LC50", "Units")

# Remove NAs
data <- na.omit(data)

# Filter into pyraclostrobin dataset
pyraclostrobin <- data %>%
  filter(
    Chemical == "Pyraclostrobin"
  )
```

# SURROGATE DATA
In this code section I will create multiple SSDs for Pyraclostrobin based on the SURROGATE data.

# Fit 4 distributions to the pyraclostrobin surrogate data to see which have best-fit
I will fit the log-normal, log-logistic, gamma, and Weibull distributions. I will then assess model fit using the Anderson-Darling (AD) statistic (lower AD means better fit). Then, I will create an SSD from the distribution with the lowest AD statistic.
```{r}
# Set the chemical to pyraclostrobin, save as a variable
single.ssd.chem <- "Pyraclostrobin"

# Create an empty list to hold the output value
individual.hc5s <- list()

#This loop calculates HC5 values from chemical-specific SSDs for each chemical in the all.chems list. It uses the best-fit method to fit the most appropriate distribution to individual chemical toxicity data (out of log-normal, log-logisitc, Weibull, and gamma distributions). The Anderson-Darling statistic is used to determine best-fit. The distribution with the lowest Anderson-Darling statistic is assigned as the "best.fit" method.
for(i in single.ssd.chem) {
  
  fit_gamma <- NULL
  best.fit <- NULL
  
  #Calculating the average toxicity value (LC50) for each species 
  IndividualSSDs <- data %>% filter(Chemical == i) %>%
    group_by(Surrogate) %>%
    summarise(
      average = geoMean(LC50), # here I am using "average" instead of "geomean" as earlier
      minimum = min(LC50),
      sd = sd(LC50),
      n = n())
  
  IndividualSSDs <- unique(IndividualSSDs) #Adding toxicity data for each chemical to a list and making sure there are no duplicates
  
  # Create intermediate data frame
  Newdf <- IndividualSSDs
  
  #Calculating the probability points for each species 
  df <- Newdf[order(Newdf$average),]
  df$frac <- ppoints(df$average, 0.5)
  df
  
  #Fit a distribution to the plotted points
  fit_llogis <- fitdist(df$average, "llogis") # fit llogis
  fit_lnorm <- fitdist(df$average, "lnorm") # fit log normal
  fit_gamma <- try(fitdist(df$average, "gamma"), silent = TRUE) # use try here as gamma often fails
  fit_weibull <- fitdist(df$average, "weibull") # fit weibull
  
  # if there is an error with the gamma distribution, fit the other three instead
  if("try-error" %in% class(fit_gamma)){
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
  }  else {
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]}
  
  #Calculate the best fit distribution
  best.fit <- fitdist(df$average, b)
  
  # Extract the estimated HC5 value
  hc5 <- quantile(best.fit, probs = 0.05)
  Estimated_HC5 <- hc5$quantiles$`p=0.05`
  
  # Bootstrap the HC5 value with upper and lower CIs
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)
  
  # This step is not necessary I am just using it to check the bootstrap is working
  bootstrap_hc5 <- quantile(fit_boot, probs = 0.05)
  
  # Save the bootstrap and upper and lower confidence intervals
  Bootstrapped_HC5 <- bootstrap_hc5$quantiles$`p=0.05`
  HC5_lower_ci <- bootstrap_hc5$quantCI[1,1]
  HC5_upper_ci <- bootstrap_hc5$quantCI[2,1]
  
  # Save the HC5 values
  hc5.table <- data.frame(i, Estimated_HC5, Bootstrapped_HC5, HC5_lower_ci, HC5_upper_ci, b, m)
  
  individual.hc5s[[i]] <- hc5.table
}

#Binding the list of individual SSD hc5 values together 
individual.hc5s <- rbindlist(individual.hc5s)
colnames(individual.hc5s) <- c("Chemical", "SSD Estimated HC5", "SSD Bootstrapped HC5", "HC5 Lower CI", "HC5 Upper CI", "SSD Dist.", "SSD AD")

# Save the pyraclostrobin HC5 as its own dataframe
pyra.surr.hc5 <- individual.hc5s
```

# Assess output of the loop
```{r}
# View the best fit table for Pyraclostrobin
best.fit.table

# Check pyraclostrobin hc5
pyra.surr.hc5
```
So, based on the results here it looks like the llogis distribution was the best-fit, as it had the lowest AD statistic.

# Extract all HC values from the best-fit distribution (HC1, HC5, HC10...HC95, HC99)
In this code chunk I will run the best-fit distribution again and extract the confidence intervals and HC values from the distribution. I will save them in a separate dataframe.
```{r}
# Open an empty list to hold the output of the loop below
HC.list <- list()

# Create a sequence increasing be 0.05
initial.seq <- seq(0.05, 0.95, by = 0.05)

# Add 0.01 and 0.99 to the beginning and end, respectively
initial.seq <- append(initial.seq, 0.99) # add .99 to end
initial.seq <- append(initial.seq, 0.01, 0) # add 0.01 to front

# Check sequence
initial.seq
length(initial.seq)

# This sequence now has all the "HC" values ranging from HC1 to HC99 by 5. Length of 21


# Create a loop that iterates through the sequence, takes the value, applies it to the ith value of the distribution (ie 0.01 = the HC1)
for (i in 1:21){ # there are 21 values between 0.01 to 0.99
  
  # Set an index to match the sequence
  index <- initial.seq[i]
  
  # Bootstrap upper and lower CIs around the value (1000 iterations)
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)

  # Save the HC value 
  HC.bootstrap <- quantile(fit_boot, probs = index)
  
  # Save HCs for that value
  HC.value.1 <- HC.bootstrap[[1]]
  HC.value.2 <- HC.value.1[1,1]
  
  # Save upper and lower CIs for that value
  HC.lower.CI <- HC.bootstrap$quantCI[1,1]
  HC.upper.CI <- HC.bootstrap$quantCI[2,1]

  # save all into table
  final.table <- data.table(index, HC.value.2, HC.upper.CI, HC.lower.CI)

  # Save the results of each run to a single element of the list
  HC.list[[i]] <- final.table
}

# Bind all list elements together into a dataframe (so each element is a row now)
HC.list <- rbindlist(HC.list)

# Save as surrogate HC data. Add in distribution used, as well as what data this is coming from
Pyra.surr.HC5.data <- HC.list

# CHange column names
colnames(Pyra.surr.HC5.data) <- c("Percentile", "HC.Value", "HC.Upper.CI", "HC.Lower.CI")

# Add in distribution and data ID
Pyra.surr.HC5.data$Distribution <- "llogis"
Pyra.surr.HC5.data$Data.ID <- "Pyraclostrobin.Surrogate"
```

We can now save this as an Excel sheet or CSV for use later. 

# Plot the SSD for the Pyraclostrobin surrogate data
```{r}
# Filter the data to only include surrogate species for Pyraclostrobin
pyra_surrogate <- pyraclostrobin %>%
  group_by(Surrogate) %>% # group by surrogate
  summarise(
    geomean = geoMean(LC50)
  )

# Remove duplicate values as we have already calculated the geomean
pyra_surrogate <- unique(pyra_surrogate)

# Create an intermediate data frame to for calculations
pyra_surr_df <- pyra_surrogate
```

### 2. Order species by toxicity values and plot
SSDs are based on a probability distribution, so the toxicity values need to be ordered from most sensitive to least sensitive.
```{r}
# Order the species by toxicity values and calculate the fraction
df <- pyra_surr_df[order(pyra_surr_df$geomean),]

# ppoints calculates a distribution of probability points
df$frac <- ppoints(df$geomean, 0.5)

# Re-order the points once again based on the distribution
df <- df[order(df$geomean), ]


# Plot the raw data
ggplot(data = df) + # the input data is the pyraclostrobin data
  geom_point(aes(x = geomean, y = frac), size = 3) + # the points are the geomeans
  geom_text(aes(x = geomean, y = frac, label = Surrogate), hjust = 1.1, size = 3) + # the text is the species label
  theme_bw() +
  scale_x_log10(limits = c(0.00005, max(df$geomean))) + # set the x axis limits
  labs(x = expression(paste('Concentration of Pyraclostrobin [ mg ', L^-1, ' ]')), 
       y = 'Fraction of species affected') # add a label to the axes
```


### 3. Fit a distribution to the data
In this example, I will be using the lognormal distribution. There are multiple other distributions that can be fitted, and it is best practice to fit a number of distributions and then use model comparisons to decide which distributions fit the best.
```{r}
# Use fitdistrplus to fit a distribution to the data
fit <- fitdist(df$geomean, "llogis") # fit a distribution to the geometric means of species

# The output gives the estimate of the mean log as well as standard errors
fit
```

### 4. Bootstrap the HC5 and CIs for the distribution
Once the distribution has been fitted, you can extract the HC5 values along with the distribution's confidence intervals.
```{r}
hc5.table <- list()
# First extract the HC5 (the 5th percentile)
hc5 <- quantile(fit, probs = 0.05)
hc5

# Then bootstrap the CIs - I am using 1000 iterations here, you can use more but then it is a longer wait time
fit_boot <- bootdist(fit, bootmethod = 'param', niter = 1000)

# As a QC check, I am extracting the HC5 from the bootstrapped value
bootstrap_hc5 <- quantile(fit_boot, probs = 0.05)

lower_ci <- bootstrap_hc5$quantCI[1,1]
upper_ci <- bootstrap_hc5$quantCI[2,1]
estimated_hc5 <- hc5$quantiles$`p=0.05`
Chemical <- "Pyraclostrobin"

# Save the HC5 values
hc5.table[[1]] <- data.frame(Chemical, estimated_hc5, lower_ci, upper_ci)

```

### 5. Generate the plot data
Now that we have extracted the HC5, we should also try and plot the data in the "classic" SSD fashion. The method is somewhat involved, but the code below should explain most of it.
```{r}
# Predict the points from the distribution on a grid of 1000

## Generate x values
newxs <- 10^(seq(log10(0.001), (log10(max(df$geomean))+1), length.out = 1000)) #creating a sequence from the smallest value to the largest value (with a bit extra so the plot does not just end at the largest value)

## Create the grid
pp <- apply(fit_boot$estim, 1, function(x) pllogis(newxs, x[1], x[2])) # using the "plnorm" function because we fit the log-normal distribution

## Make the grid a data frame
bootdat <- data.frame(pp) # each column is the result from a bootstrap sample

## add x-values
bootdat$newxs <- newxs
require(reshape2) # needed for data manipulation

## bring to long format
bootdat <- melt(bootdat, id.vars = 'newxs')

## get Ci from bootstraps
cis <- apply(pp, 1, quantile, c(0.025, 0.975))

## Label the lower and upper confidence intervals
rownames(cis) <- c('lwr' ,'upr')

## Save the x values and y values into a dataframe
pdat <- data.frame(newxs, py = pllogis(newxs, shape = fit$estimate[1], scale = fit$estimate[2]))

## add CI
pdat <- cbind(pdat, t(cis))

# add x coordinates for species names from fitted values
df$fit <- 10^(log10(qllogis(df$frac, shape = fit$estimate[1], scale = fit$estimate[2])) - 0.4)
```

### 6. Plot the data
Now, use ggplot to plot the data. I have commented what each line of the plot code means
```{r}
# plot it!
pyra.surr.ssd.plot <- ggplot()+
  geom_line(data = bootdat, aes(x = newxs, y = value, group = variable), col = 'steelblue', alpha = 0.05) +  # this is the 1000s of "distributions" we fitted onto the grid earlier
  geom_point(data = df, aes(x = geomean, y = frac)) + # this adds in the species points from the original data
  geom_line(data = pdat, aes(x = newxs, y = py), col = 'red') + # this is the true fit line
  geom_line(data = pdat, aes(x = newxs, y = lwr), linetype = 'dashed') + # upper confidence interval
  geom_line(data = pdat, aes(x = newxs, y = upr), linetype = 'dashed') + # lower confidence interval
  geom_text(data = df, aes(x = fit, y = frac, label = Surrogate), hjust = 0.8, size = 3)+
  theme_bw() + # changes plot theme
  scale_x_log10() + # log scale on x axis
  labs(x = expression(paste('Pyraclostrobin (surrogate data) [ mg ', L^-1, ' ]')), 
       y = 'Proportion of species affected') # adds in labels for x and y axis
pyra.surr.ssd.plot
```




# PYRACLOSTROBIN PREDICTION DATA

# Fit 4 distributions to the pyraclostrobin surrogate data to see which have best-fit
I will fit the log-normal, log-logistic, gamma, and Weibull distributions. I will then assess model fit using the Anderson-Darling (AD) statistic (lower AD means better fit). Then, I will create two SSDs using the two distributions with the lowest AD statistic.
```{r}
# Set the chemical to pyraclostrobin, save as a variable
single.ssd.chem <- "Pyraclostrobin"

# Create an empty list to hold the output value
individual.hc5s <- list()

#This loop calculates HC5 values from chemical-specific SSDs for each chemical in the all.chems list. It uses the best-fit method to fit the most appropriate distribution to individual chemical toxicity data (out of log-normal, log-logisitc, Weibull, and gamma distributions). The Anderson-Darling statistic is used to determine best-fit. The distribution with the lowest Anderson-Darling statistic is assigned as the "best.fit" method.
for(i in single.ssd.chem) {
  
  fit_gamma <- NULL
  best.fit <- NULL
  
  #Calculating the average toxicity value (LC50) for each species 
  IndividualSSDs <- data %>% filter(Chemical == i) %>%
    group_by(Prediction) %>%
    summarise(
      average = geoMean(LC50), # here I am using "average" instead of "geomean" as earlier
      minimum = min(LC50),
      sd = sd(LC50),
      n = n())
  
  IndividualSSDs <- unique(IndividualSSDs) #Adding toxicity data for each chemical to a list and making sure there are no duplicates
  
  # Create intermediate data frame
  Newdf <- IndividualSSDs
  
  #Calculating the probability points for each species 
  df <- Newdf[order(Newdf$average),]
  df$frac <- ppoints(df$average, 0.5)
  df
  
  #Fit a distribution to the plotted points
  fit_llogis <- fitdist(df$average, "llogis") # fit llogis
  fit_lnorm <- fitdist(df$average, "lnorm") # fit log normal
  fit_gamma <- try(fitdist(df$average, "gamma"), silent = TRUE) # use try here as gamma often fails
  fit_weibull <- fitdist(df$average, "weibull") # fit weibull
  
  # if there is an error with the gamma distribution, fit the other three instead
  if("try-error" %in% class(fit_gamma)){
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]
  }  else {
    ll <- gofstat(fit_llogis)
    ln <- gofstat(fit_lnorm)
    g <- gofstat(fit_gamma)
    w <- gofstat(fit_weibull)
    
    #Fit the best distribution to the data; identify it by the lowest anderson darling statistic
    a <- unlist(c(ll[8], ln[8], g[8], w[8]))
    best.fit.table <- data.table(c("llogis", "lnorm", "gamma", "weibull"), a)
    m <- min(a)
    b <- best.fit.table$V1[best.fit.table$a == m]}
  
  #Calculate the best fit distribution
  best.fit <- fitdist(df$average, b)
  
  # Extract the estimated HC5 value
  hc5 <- quantile(best.fit, probs = 0.05)
  Estimated_HC5 <- hc5$quantiles$`p=0.05`
  
  # Bootstrap the HC5 value with upper and lower CIs
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)
  
  # This step is not necessary I am just using it to check the bootstrap is working
  bootstrap_hc5 <- quantile(fit_boot, probs = 0.05)
  
  # Save the bootstrap and upper and lower confidence intervals
  Bootstrapped_HC5 <- bootstrap_hc5$quantiles$`p=0.05`
  HC5_lower_ci <- bootstrap_hc5$quantCI[1,1]
  HC5_upper_ci <- bootstrap_hc5$quantCI[2,1]
  
  # Save the HC5 values
  hc5.table <- data.frame(i, Estimated_HC5, Bootstrapped_HC5, HC5_lower_ci, HC5_upper_ci, b, m)
  
  individual.hc5s[[i]] <- hc5.table
}

#Binding the list of individual SSD hc5 values together 
individual.hc5s <- rbindlist(individual.hc5s)
colnames(individual.hc5s) <- c("Chemical", "SSD Estimated HC5", "SSD Bootstrapped HC5", "HC5 Lower CI", "HC5 Upper CI", "SSD Dist.", "SSD AD")

# Save the pyraclostrobin HC5 as its own dataframe
pyra.pred.best.fit.hc5 <- individual.hc5s
```


# Assess output of the loop
```{r}
# View the best fit table for pyraclostrobin
best.fit.table

# Check pyraclostrobin hc5
pyra.pred.best.fit.hc5
```

So, based on the results here it looks like the llogis distribution was the best-fit, as it had the lowest AD statistic.

# Extract all HC values from the best-fit distribution (HC1, HC5, HC10...HC95, HC99)
In this code chunk I will run the best-fit distribution again and extract the confidence intervals and HC values from the distribution. I will save them in a separate dataframe.
```{r}
# Open an empty list to hold the output of the loop below
HC.list <- list()

# Create a sequence increasing be 0.05
initial.seq <- seq(0.05, 0.95, by = 0.05)

# Add 0.01 and 0.99 to the beginning and end, respectively
initial.seq <- append(initial.seq, 0.99) # add .99 to end
initial.seq <- append(initial.seq, 0.01, 0) # add 0.01 to front

# Check sequence
initial.seq
length(initial.seq)

# This sequence now has all the "HC" values ranging from HC1 to HC99 by 5. Length of 21


# Create a loop that iterates through the sequence, takes the value, applies it to the ith value of the distribution (ie 0.01 = the HC1)
for (i in 1:21){ # there are 21 values between 0.01 to 0.99
  
  # Set an index to match the sequence
  index <- initial.seq[i]
  
  # Bootstrap upper and lower CIs around the value (1000 iterations)
  fit_boot <- bootdist(best.fit, bootmethod = 'param', niter = 1000)

  # Save the HC value 
  HC.bootstrap <- quantile(fit_boot, probs = index)
  
  # Save HCs for that value
  HC.value.1 <- HC.bootstrap[[1]]
  HC.value.2 <- HC.value.1[1,1]
  
  # Save upper and lower CIs for that value
  HC.lower.CI <- HC.bootstrap$quantCI[1,1]
  HC.upper.CI <- HC.bootstrap$quantCI[2,1]

  # save all into table
  final.table <- data.table(index, HC.value.2, HC.upper.CI, HC.lower.CI)

  # Save the results of each run to a single element of the list
  HC.list[[i]] <- final.table
}

# Bind all list elements together into a dataframe (so each element is a row now)
HC.list <- rbindlist(HC.list)

# Save as pred HC data. Add in distribution used, as well as what data this is coming from
pyra.pred.hc.data <- HC.list

# CHange column names
colnames(pyra.pred.hc.data) <- c("Percentile", "HC.Value", "HC.Upper.CI", "HC.Lower.CI")

# Add in distribution and data ID
pyra.pred.hc.data$Distribution <- "llogis"
pyra.pred.hc.data$Data.ID <- "Pyraclostrobin.Prediction"
```

# Plot the SSD for the pyraclostrobin prediction data
```{r}
# Filter the data to only include pred species for pyraclostrobin
pyra_pred <- pyraclostrobin %>%
  group_by(Prediction) %>% # group by prediction
  summarise(
    geomean = geoMean(LC50)
  )

# Remove duplicate values as we have already calculated the geomean
pyra_pred <- unique(pyra_pred)

# Create an intermediate data frame to for calculations
pyra_pred_df <- pyra_pred
```

### 2. Order species by toxicity values and plot
SSDs are based on a probability distribution, so the toxicity values need to be ordered from most sensitive to least sensitive.
```{r}
# Order the species by toxicity values and calculate the fraction
df <- pyra_pred_df[order(pyra_pred_df$geomean),]

# ppoints calculates a distribution of probability points
df$frac <- ppoints(df$geomean, 0.5)

# Re-order the points once again based on the distribution
df <- df[order(df$geomean), ]


# Plot the raw data
ggplot(data = df) + # the input data is the pyraclostrobin data
  geom_point(aes(x = geomean, y = frac), size = 3) + # the points are the geomeans
  geom_text(aes(x = geomean, y = frac, label = Prediction), hjust = 1.1, size = 3) + # the text is the species label
  theme_bw() +
  scale_x_log10(limits = c(0.005, max(df$geomean))) + # set the x axis limits
  labs(x = expression(paste('Concentration of Pyraclostrobin [ mg ', L^-1, ' ]')), 
       y = 'Fraction of species affected') # add a label to the axes
```



### 3. Fit a distribution to the data
In this example, I will be using the lognormal distribution. There are multiple other distributions that can be fitted, and it is best practice to fit a number of distributions and then use model comparisons to decide which distributions fit the best.
```{r}
# Use fitdistrplus to fit a distribution to the data
fit <- fitdist(df$geomean, "llogis") # fit a distribution to the geometric means of species

# The output gives the estimate of the mean log as well as standard errors
fit
```



### 5. Generate the plot data
Now that we have extracted the HC5, we should also try and plot the data in the "classic" SSD fashion. The method is somewhat involved, but the code below should explain most of it.
```{r}
# Predict the points from the distribution on a grid of 1000

## Generate x values
newxs <- 10^(seq(log10(0.0001), (log10(max(df$geomean))+1.5), length.out = 1000)) #creating a sequence from the smallest value to the largest value (with a bit extra so the plot does not just end at the largest value)

## Create the grid
pp <- apply(fit_boot$estim, 1, function(x) pllogis(newxs, x[1], x[2])) # using the "plnorm" function because we fit the log-normal distribution

## Make the grid a data frame
bootdat <- data.frame(pp) # each column is the result from a bootstrap sample

## add x-values
bootdat$newxs <- newxs
require(reshape2) # needed for data manipulation

## bring to long format
bootdat <- melt(bootdat, id.vars = 'newxs')

## get Ci from bootstraps
cis <- apply(pp, 1, quantile, c(0.025, 0.975))

## Label the lower and upper confidence intervals
rownames(cis) <- c('lwr' ,'upr')

## Save the x values and y values into a dataframe
pdat <- data.frame(newxs, py = pllogis(newxs, shape = fit$estimate[1], scale = fit$estimate[2]))

## add CI
pdat <- cbind(pdat, t(cis))

# add x coordinates for species names from fitted values
df$fit <- 10^(log10(qllogis(df$frac, shape = fit$estimate[1], scale = fit$estimate[2])) - 0.4)
```

### 6. Plot the data
Now, use ggplot to plot the data. I have commented what each line of the plot code means
```{r}
# plot it!
pyra.pred.ssd.plot <- ggplot()+
  geom_line(data = bootdat, aes(x = newxs, y = value, group = variable), col = 'steelblue', alpha = 0.05) +  # this is the 1000s of "distributions" we fitted onto the grid earlier
  geom_point(data = df, aes(x = geomean, y = frac)) + # this adds in the species points from the original data
  geom_line(data = pdat, aes(x = newxs, y = py), col = 'red') + # this is the true fit line
  geom_line(data = pdat, aes(x = newxs, y = lwr), linetype = 'dashed') + # upper confidence interval
  geom_line(data = pdat, aes(x = newxs, y = upr), linetype = 'dashed') + # lower confidence interval
  geom_text(data = df, aes(x = fit, y = frac, label = Prediction), hjust = 1, size = 3) +
  theme_bw() + # changes plot theme
  scale_x_log10() + # log scale on x axis
  labs(x = expression(paste('Pyraclostrobin (Pred data) [ mg ', L^-1, ' ]')), 
       y = 'Proportion of species affected') # adds in labels for x and y axis
pyra.pred.ssd.plot
```

# Save the SSDs and tables
```{r}
# Surrogate data saving
write.csv(Pyra.surr.HC5.data, file = "pyra_surrogate_data.csv")

# Save the surrogate SSD image
tiff("Pyra_surr_SSD.tiff", units = "in", width = 7.5, height = 7, res = 300) # load an empty tiff file with these dimensions
pyra.surr.ssd.plot # put in the final results plot
dev.off() # close graphics so it saves

# Pred data saving
write.csv(pyra.pred.hc.data, file = "pyra_pred_data.csv")

# Save the pred SSD image
tiff("Pyra_pred_SSD.tiff", units = "in", width = 7.5, height = 7, res = 300) # load an empty tiff file with these dimensions
pyra.pred.ssd.plot # put in the final results plot
dev.off() # close graphics so it saves
```

# RUn all code
```{r}

```

# Add the LC 50 estimate from our curve; here, I modified the mg/L LC50 estimates by the same 
```{r}
bootdat$lc50bcf<-bootdat$newxs * (0.05*(10^3.99))

dfn<-df
dfn[,c(2,4)]<-dfn[,c(2,4)]* (0.05*(10^3.99))

pdatn<-pdat
pdatn[,1]<-pdatn[,1]*(0.05*(10^3.99))

pyra.pred.ssd.plot.bcf <- ggplot()+
  geom_line(data = bootdat, aes(x = lc50bcf, y = value, group = variable), col = 'steelblue', alpha = 0.05) +  # this is the 1000s of "distributions" we fitted onto the grid earlier
  geom_point(data = dfn, aes(x = geomean, y = frac)) + # this adds in the species points from the original data
  geom_line(data = pdatn, aes(x = newxs, y = py), col = 'red') + # this is the true fit line
  geom_line(data = pdatn, aes(x = newxs, y = lwr), linetype = 'dashed') + # upper confidence interval
  geom_line(data = pdatn, aes(x = newxs, y = upr), linetype = 'dashed') + # lower confidence interval
  geom_text(data = dfn, aes(x = fit, y = frac, label = Prediction), hjust = 1.2, size = 3) +
  theme_bw() + # changes plot theme
  scale_x_log10() + # log scale on x axis
  labs(x = expression(paste('Pyraclostrobin (Pred data) [ ug ', g^-1, ' ]')), 
       y = 'Proportion of species affected') # adds in labels for x and y axis

pyra.pred.ssd.plot.bcf


pyra.pred.ssd.plot.fin<-pyra.pred.ssd.plot.bcf +  
  geom_point(aes(x=log10(6),y=0.50),colour="red") +
  annotate("text", x = log10(1.6), y = 0.50, label = "Estimated LD50 Pyraclostrobin", size=3)

pyra.pred.ssd.plot.fin


pyra.pred.hc.data$HC.Value *(0.05*(10^3.99))
pyra.pred.hc.data$HC.Upper.CI*(0.05*(10^3.99))

```
















